---
title: "Pragma Analysis"
author: "Jakob & Kilian"
format:
  html:
    self-contained: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
    code-fold: true
    code-tools: true
    code-link: true
    toc: true
    df-print: paged
    crossrefs-hover: true	

editor: visual
---

# What Do I Do?

This document produces an analysis using LCA and Hierarchical Clustering with variable class/cluster numbers (k). It relies on data in the shape of sequence_data_for_kilian.csv with an aud.date column

The Results of the Models are visualized for easy interpretability

## LCA on binary treatment sequences

First, we import our preprocessed Data containing treatment series on a relative timescale

```{r}
#| message: false

library(here)
library(venneuler)
library(dendextend)
library(fs)
library(poLCA) # this package is a nightmare. It loads a select() function which overwrites tidyverse select() if tidyverse is loaded first or already attached to namespace
library(vegan)
library(timetk)
library(tidyverse)
library(here)
library(furrr)
library(vroom)
here::i_am("AnalyzePragmaDataQuartersAUD_NoRelTime.qmd")

```

```{r}
# set analysis parameters
analysis_vars = c("qwt", "inpat", "reha", "psych_short","psych_full", "medi", "bado") # set the variables which should be plotted and used within the analysis.
obs_period = "24m" # observational period
resol = "quarter" # time resolution for plotting purposes starting from aud date. 
# possible vals: "day", "week", "month", "quarter", "halfyear", "year"
save = T # save transformed dataframe as cache in order to reexecute script faster
load_if_possible = F # if saved transformed df is found, load instead of compute
render = T # overrides console prompting for laod if possible in order to render document
classnum = 6# Which model should be used for subsequent analysis? (number equals classes of the desired model)
```

```{r}
getwd()
dat = read_rds(here("input","sequence_data_240516","4_data_AUD diagnosis and intervention sequences_2024-05-16.rds")) 
# create an interv_id running within treatment type instead of across treatment types
dat = dat %>% left_join(dat %>%  
  select(pragmaid, period, interv.type, interv_id) %>%
  drop_na() %>%
  group_by(pragmaid, period, interv.type) %>%
  mutate(interv_id_inner = 1:n()) %>%
  ungroup()
)

source(here("upsample_daily_utils.r")) # load up/downsampling and utility functions



# this takes a pretty long time (5minutes) on machine with 16 logical cores and 32gig ram. Significantly speeds up when all indivs who had no intervention are excluded from data before upsampling. # Results can be also precomputed via save and load_if_possible/ render

dat_qwt = get_treatment_series_at_resolution(dat,
                                             period = obs_period, # observation period
                                             resol = resol, # timestep resolution
                                             event = "aud", # event to start treatment series. currently does nothing (always set to aud)
                                             save = T, # save result when computed?
                                             load_if_possible = F, # load if same config exists in cache folder, prompts user in order to check if right file is laoded
                                             render = T, # forces load without prompting (ovverrides prompt and just chooses the most likely one)
                                             only_intervs = T) %>% 
  filter(interv.any.allquarters == T) # only use cases where an intervention happened because LCA has problems fitting all the zero cases



```

Pivoting it into a wide format implicitly creates time sensitive dummy variables:

```{r}
# transform into wide format, such that the time is coded in dummy variables (qwt_t1, qwt_t2 ...)
dat_qwt_wide = dat_qwt %>%
  group_by(pragmaid, rel_time) %>% 
  mutate(psych = any(psych_short, psych_full)) %>%
  ungroup() %>% 
  select(pragmaid,
         rel_time, 
         all_of(analysis_vars)
         ) %>% 
  pivot_wider(id_cols = pragmaid,
              names_from = rel_time,
              values_from = all_of(analysis_vars)) %>% 
  arrange(pragmaid)
#head(dat_qwt_wide)




```

For the poLCA package, data must occur in categorical levels, in increments from 1 to max level (in our case 2 since data is binary)

Now, create the formula and run LCA models on the dataset. We will try a 2-7 class solutions:

```{r}
#| label: LCA-Outputs

f  = as.formula(paste0("cbind(",paste(analysis_vars, collapse = ","), ")~1" ))
# should equal:
# f = cbind(qwt, reha, medi, psych_short, psych_full, inpat, bado) ~ 1 # formula for LCA clustering

# poLCA needs variables to increment from 1 to max level
# 1 = No
# 2 = Yes
dat_qwt_num = dat_qwt %>%
  group_by(pragmaid) %>%
  summarize_at(analysis_vars, ~any(.x) + 1)


set.seed(341)
m2 = poLCA::poLCA(f, dat_qwt_num, nclass = 2, graph = T, maxiter = 100000, nrep = 5)
m3 = poLCA::poLCA(f, dat_qwt_num, nclass = 3, graph = T, maxiter = 100000, nrep = 5)
m4 = poLCA::poLCA(f, dat_qwt_num, nclass = 4, graph = T, maxiter = 100000, nrep = 5)
m5 = poLCA::poLCA(f, dat_qwt_num, nclass = 5, graph = T, maxiter = 100000, nrep = 5)
m6 = poLCA::poLCA(f, dat_qwt_num, nclass = 6, graph = T, maxiter = 100000, nrep = 5)
m7 = poLCA::poLCA(f, dat_qwt_num, nclass = 7, graph = T, maxiter = 100000, nrep = 5)

# choose the n class solution for both models, the lca and the hierarchical clusterings
dat_qwt_num$predclass = eval(parse(text = paste0("m", classnum, "$predclass")))
dat_qwt_num %>% 
  select(pragmaid, predclass) %>%
  write_csv(here("output", "sequence_data_24m_monthly_lca_results.csv"))

```

## Visualize LCA results without 3D

Take a look at the proportion of individuals using a service over time, for the different clusters identified by the lca. This corresponds somewhat to binary "typical" group trajectories.

```{r}
#| title: Naive Frequency Visualization of LCA Results
#| warning: false
#| include: false

label_fn = function(dat){

frac = data.frame(pragmaid = dat$pragmaid, predclass = dat$predclass %>% as.factor()) %>%
  group_by(predclass) %>% 
  summarize(n=n_distinct(pragmaid)) %>%
  mutate(frac = str_c(round(n/sum(n),3)*100, "%"), 
         predclass = as.integer(predclass))
  #print(frac)
  res = c()
  for(i in 1:nrow(frac)){
  res[i] = paste0("C" ,
                  frac[i, ]$predclass,
                  ", n = ",
                  frac[i, ]$n,
                  ", (",
                  frac[i, ]$frac,
                  ")"
  )
  
  }
  names(res) = frac %>% select(predclass) %>% pull()
  return(res) 
}

dat_qwt_num %>%
  select(pragmaid, predclass) %>%
  left_join(dat_qwt) %>%
  group_by(predclass, rel_time) %>% 
  summarize_at(all_of(analysis_vars), ~ sum(.x)/length(.x) ) %>% 
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x = rel_time, y = value*100, col = as.factor(predclass))) +
  geom_line(linewidth = 1.2) +
  facet_grid(~variable, scales = "free_y") +
  labs(y = "[%] Individuals using Service", col = "Latent Class")

```

Looking at the variables from a group perspective results in the following plot:

```{r}
#| label: fig-prop-pp-viz
#| warnig: false
#| message: false

#dat_qwt_num$predclass <- factor(dat_qwt_num$predclass, levels = c(4,2,1,3,5,6))

dat_qwt_num %>%
  select(pragmaid, predclass) %>%
  left_join(dat_qwt) %>% 
  group_by(predclass, rel_time) %>% 
  summarize_at(all_of(analysis_vars), ~ sum(.x)/length(.x), ) %>% 
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x = rel_time, y = value*100, col = variable)) +
  geom_line(linewidth = 1.2) +
  ggthemes::scale_color_gdocs() +
  facet_grid(.~predclass, scales = "free_y",labeller = as_labeller(label_fn(dat_qwt_num))) +
  labs(x = "number of quarters after AUD diagnosis",
       y = "[%] Individuals using Service")

ggsave(paste0("output/","figures/","fig_classes_lineplot_class6_",Sys.Date(),".png"), width = 10, height = 6)


```

```{r}



#TODO: Explore mosaic plots{
#TODO: Zeitliche auflösung der zeitlichen Kreuztabellen durch Variablen ersetzen - 
# TODO: Reha-qwt zusammenhang "Nicht fälle"! mit berücksichtigen als Spalte/Zeile
#TODO: Quarter Annahme raus nehmen und behandlungen durch tatsächliche interventions IDs ersetzen
#TODO: BLRT und Entropy berechnen!
# TODO add 2-4 and 5+ group into multiple interv chart


dat_pred = dat_qwt_num %>%
  select(pragmaid, predclass) %>%
  right_join(dat %>%
              filter(period == obs_period,
                     !is.na(interv_id_inner),
                     interv.any ==T)
             )





get_categorical_interv_num = function(num_intervs){
  if(num_intervs == 1) return("1")
  if(num_intervs > 1 & num_intervs <= 4) return("2-4")
  if(num_intervs > 4) return("5+")
}
get_categorical_interv = Vectorize(get_categorical_interv_num)

dat_pred %>% 
  group_by(predclass) %>% 
  mutate(n_class = n_distinct(pragmaid)) %>% 
  ungroup() %>% 
  group_by(pragmaid, predclass, interv.type) %>%
  mutate(num_intervs = n(), more_than_one_interv = get_categorical_interv(num_intervs)) %>% 
  group_by(predclass, interv.type) %>% 
  mutate(n_had_interv = n_distinct(pragmaid)) %>% 
  group_by(predclass, interv.type, more_than_one_interv) %>% 
  summarize(n = n_distinct(pragmaid), frac = n/mean(n_had_interv)) %>% 
  ggplot(aes(x = interv.type, y = frac * 100)) +
  geom_col(aes(fill = more_than_one_interv)) +
  facet_wrap(~paste("Latent Class", predclass)) +
 # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Intervention", y = "Anteil Personen innerhalb Intervention", fill = "Anzahl Interventionen") + 
  coord_flip()

ggsave(paste0("output/","figures/","fig_classes_barplot.png"), width = 10, height = 6)


```

```{r}

  
dat_pred2 = dat_pred %>% select(pragmaid, predclass) %>% distinct() %>%  right_join(dat_qwt %>%
  group_by(pragmaid) %>%
  summarize_at(analysis_vars, ~any(.x))) 


# helper function  
get_overlap = function(dat,
                       cls,
                       var1,
                       var2,
                       perspective = c("class", "intervention")){

  
  perspective = match.arg(perspective)
  if(perspective == "class"){
  overlaps = dat %>%
    ungroup() %>% 
    filter(predclass == cls) %>% 
    select(pragmaid, all_of(c(var1,var2))) %>% 
    group_by(pragmaid) %>% 
    summarize(overlap = all(pick(var1),  pick(var2)))
  }
  else{
    dat = dat[c(dat[var1] == TRUE), ]
    overlaps = dat %>%
    ungroup() %>% 
    filter(predclass == cls) %>% 
    select(pragmaid, all_of(c(var1,var2))) %>% 
    group_by(pragmaid) %>% 
    summarize(overlap = all(pick(var1),  pick(var2)))
  }
  
  overlap = sum(overlaps$overlap)/nrow(overlaps)

  # res = data.frame(var = var1, val = overlap) 
  # names(res)[2] = var2
  return(overlap)
}
# helper function end


get_inter_variable_overlaps = function(dat,
                                       cls,
                                       analysis_vars,
                                       perspective =  c("class", "intervention")){
  
perspective = match.arg(perspective)


resresres = data.frame()
for(v1 in analysis_vars){
  resres = data.frame(var = v1)
  
  for(v2 in analysis_vars){
    res = data.frame(val = get_overlap(dat,
                                       cls,
                                       v1,
                                       v2,
                                       perspective = perspective))
    names(res) = v2
    resres = cbind(resres, res)
  }
  
  resresres = rbind(resresres, resres)
}
resresres$predclass = cls
return(resresres)
}





overlaps_class_persp = map_dfr(1:classnum,
                               ~ get_inter_variable_overlaps(
                                            dat_pred2,
                                            cls =.x, 
                                            analysis_vars,
                                            perspective = "class"))


overlaps_interv_persp = map_dfr(1:classnum, 
                                ~ get_inter_variable_overlaps(
                                            dat_pred2,
                                            cls =.x, 
                                            analysis_vars,
                                            perspective = "intervention"))

# TODO: Make the same for all without class

overlaps_class_persp %>%
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "var2", 
               values_to = "val") %>% 
  mutate(var = as.factor(var), var2 = as.factor(var2)) %>% 
  ggplot(aes(x = reorder(var, desc(var)), y = var2, fill = val)) +
  geom_tile() +
  facet_wrap(~paste0("Latent Class ", predclass), scales = "free") +
  geom_text(aes(label = paste0(round(val * 100, 0), "%")), size = 2) +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0)) +
  scale_x_discrete(limits = rev(levels(var))) +
  labs(x = "Anteil Inanspruchnahmen weiterer Intervention",
       y = "Intervention", 
       fill = "Anteil Klasse[%]")

# TODO: Add a column where the absolute percantage of class who did intervention y is displayed
overlaps_interv_persp %>%
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "var2", 
               values_to = "val") %>% 
    mutate(var = as.factor(var), var2 = as.factor(var2), 
           val = ifelse(is.nan(val), 0, val)) %>% 
  ggplot(aes(x = reorder(var, desc(var)), y = var2, fill = val)) +
  geom_tile() +
  facet_wrap(~paste0("Latent Class ", predclass), scales = "free") +
  geom_text(aes(label = paste0(round(val * 100, 0), "%")), size = 1.5) +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0)) +
  scale_x_discrete(limits = rev(levels(var))) +
  labs(x = "Intervention",
       y = "Anteil Inanspruchnahme weiterer Intervention",
       fill = "Anteil X[%]")

```

```{r, include = F}


dat_pred = dat_qwt_num %>% select(pragmaid, predclass) %>% right_join(dat_qwt)

lookup =  dat_pred %>% group_by(predclass) %>% summarize(n_ids=n_distinct(pragmaid))
  
dat_pred %>% 
  group_by(pragmaid, predclass) %>% 
  summarize_at(analysis_vars, ~sum(.x)) %>%
  pivot_longer(cols = all_of(analysis_vars), names_to = "var", values_to = "n_treats") %>% 
  group_by(var, n_treats, predclass) %>% 
  summarize(n = n()) %>% left_join(lookup, by = c("predclass" ="predclass")) %>% 
  ungroup() %>% 
  mutate(frac = n/n_ids) %>% 
  select(var,n_treats, predclass, frac) %>% 
  ggplot(aes(x = n_treats, y = var, fill = frac)) +
  geom_tile() + facet_wrap(~predclass, scales = "free") +
  geom_text(aes(label = paste0(round(frac * 100, 0), "%")), size = 2) +
  scale_fill_viridis_c() +
  labs(x = "Anzahl der Inanspruchnahmen innerhalb von 2 Jahren", y = "Intervention") + 
  scale_x_discrete()







```

```{r, include=FALSE}
  
# 
# 
# get_variable_time_overlaps = function(dat, var1, var2, clss){
#   var_a = ensym(var1)
#   var_b = ensym(var2)
#   
# 
# tst = dat_pred %>%
#   filter(predclass == clss) %>%
#   select(pragmaid, rel_time, all_of(c(var1,var2))) %>% filter(!!var_a == T|!!var_b==T) %>% 
#   arrange(rel_time) %>% 
#   pivot_wider(names_from = rel_time, values_from = all_of(c(var1, var2)), values_fill = F )
# 
# tmp = data.frame(time_var = names(tst) %>% str_subset(var2))
# for(nam in names(tst) %>% str_subset(var1)){
#   tmp2 = data.frame()
#   for(nam2 in names(tst) %>% str_subset(var2)){
#     tmp3 = data.frame(val = length(intersect(
#                       tst$pragmaid[tst[[nam]]],
#                       tst$pragmaid[tst[[nam2]]]
#                           ))
#                       )
#     tmp2 = rbind(tmp2, tmp3)
#     
#   }
#   tmp = cbind(tmp, tmp2)
# }
# names(tmp) = c("var_time", names(tst) %>% str_subset(var1))
# return(tmp)
# }
# 
# 
# 
# ttst = venngardium_leviosa(dat_pred, varname = "psych_short", class = 1, limit = 2, showplot = T)
# 
# venngardium_leviosa(dat_pred, varname = "inpat", class = 2, limit = 4, showplot = T)
# 
# 
# 
# 
# 
# 
# get_variable_time_overlaps(dat_pred,"qwt" ,"reha",2)
# get_variable_time_overlaps(dat_pred,"qwt" ,"psych_short",2)
# 
# 
# View(get_variable_time_overlaps(dat_pred,"inpat" ,"qwt",3))
# View(get_variable_time_overlaps(dat_pred,"inpat" ,"reha",3))
# View(get_variable_time_overlaps(dat_pred,"qwt" ,"reha",3))
# 
# 
# get_variable_time_overlaps(dat_pred,"inpat" ,"qwt",4)
# 
# 



```

We can display the same information with a Heatmap

```{r}
#| title: Heatmap of LCA Results
#| warning: false

# create a heatmap of the binary data used in the LCA
dat_qwt_num %>%
  select(pragmaid, predclass) %>%
  left_join(dat_qwt) %>% 
  group_by(predclass, rel_time) %>% 
  summarize_at(all_of(analysis_vars), ~ round(sum(.x)/length(.x), 3)*100, ) %>% 
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x = rel_time, y = predclass, fill = value)) + 
  geom_tile(show.legend = F) +
  geom_text(aes(label = paste0(round(value, 0),"%")), size = 2.5) +
  theme_minimal() +
  scale_fill_viridis_c() +
  facet_wrap(~variable)


```

## Hierarchical Clustering via Jaccard (dis)similarity

In order to cluster the Data in a hierarchical structure, we construct jaccard dissimilarity (distance) matrices, which we can feed into the hclust function.

```{r}
#| title: Prepare Distance Data

# we can use the vegan package to get jaccard dissimilarity metric. 
# or the builtin dist() function. 




dat_qwt_sum = dat_qwt %>%
  group_by(pragmaid) %>% 
  summarize(across(analysis_vars, ~any(.x)))
  
dist1 = dist(dat_qwt_sum %>% dplyr::select(all_of(analysis_vars)), method = "binary")
#identical 
dist2 = vegdist(dat_qwt_sum %>% dplyr::select(all_of(analysis_vars)), method = "jaccard", binary = TRUE)

```

Now we can apply some different hierarchical clustering methods and visualize the results via dendrograms.

```{r}
#| title: Hierarchical Clustering and Dendrogram visualization
#| message: false

c1 = hclust(dist1, method = "ward.D2")
plot(c1)

#c2 = hclust(dist2, method = "average") # doesnt work when there are rows with FALSE only
#plot(c2)

c3 = hclust(dist1, method = "complete")
plot(c3)



```

I Liked the clusters in Method ward.D2 (c1) the best and will continue the analysis with these clusters. In order to maintain comparability with our lca results, I will remain at a `r paste(length(unique(dat_qwt_num$predclass)))` class solution.

```{r}
#| title: Metric Visualizations
#| message: false
#| warning: false

dend_c1 = as.dendrogram(c1)
col_dend_c1 = color_branches(dend_c1, k = length(unique(dat_qwt_num$predclass)))
plot(col_dend_c1)
cuts = cutree(c1, k= length(unique(dat_qwt_num$predclass)))

```

Now we can look at the proportion of individuals using a service over time, for the different clusters identified by the hierarchical clustering. This corresponds somewhat to binary "typical" group trajectories.

```{r}
#| title: Proportion (%) Table
#| warnig: false
#| message: false

frac = data.frame(clust = cuts %>% as.factor()) %>%
  group_by(clust) %>% 
  summarize(n=n()) %>%
  mutate(frac = str_c(round(n/sum(n),3)*100, "%"))

frac %>%
  knitr::kable()
```

```{r}
#| title: Proportion (%) Visualizations
#| warnig: false
#| message: false
#| include: false
dat_qwt_wide = dat_qwt_wide %>%
  mutate(cluster = cuts)

dat_qwt_wide %>%
  select(pragmaid, cluster) %>% 
  left_join(dat_qwt) %>% 
  group_by(cluster, rel_time) %>% 
  summarize_at(all_of(analysis_vars), ~ sum(.x)/length(.x), ) %>% 
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x = rel_time, y = value*100, col = as.factor(cluster))) +
  geom_line(linewidth = 1.2) +
  facet_wrap(~variable, scales = "free_y") +
  labs(y = "[%] Individuals using Service", col = "Cluster")

```

Swapping the variables with the clusters results in:

```{r}
#| title: Proportion (%) Visualizations group pp
#| warnig: false
#| message: false

label_fn2 = function(dat){

frac = data.frame(pragmaid = dat$pragmaid, cluster = dat$cluster %>% as.factor()) %>%
  group_by(cluster) %>% 
  summarize(n=n_distinct(pragmaid)) %>%
  mutate(frac = str_c(round(n/sum(n),3)*100, "%"), 
         predclass = as.integer(cluster))
  #print(frac)
  res = c()
  for(i in 1:nrow(frac)){
  res[i] = paste0("C" ,
                  frac[i, ]$cluster,
                  ", n = ",
                  frac[i, ]$n,
                  " (",
                  frac[i, ]$frac,
                  ")"
  )
  
  }
  names(res) = frac %>% select(predclass) %>% pull()
  return(res) 
}

dat_qwt_wide %>%
  select(pragmaid, cluster) %>% 
  left_join(dat_qwt) %>% 
  group_by(cluster, rel_time) %>% 
  summarize_at(all_of(analysis_vars), ~ sum(.x)/length(.x), ) %>% 
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x = rel_time, y = value*100, col = variable)) +
  geom_line(linewidth = 1.2) +
  facet_grid(.~cluster, scales = "free_y", labeller = as_labeller(label_fn2(dat_qwt_wide))) +
  labs(y = "[%] Individuals using Service")
```

```{r}


#TODO: Explore mosaic plots{
#TODO: Zeitliche auflösung der zeitlichen Kreuztabellen durch Variablen ersetzen - 
# TODO: Reha-qwt zusammenhang "Nicht fälle"! mit berücksichtigen als Spalte/Zeile
#TODO: Quarter Annahme raus nehmen und behandlungen durch tatsächliche interventions IDs ersetzen
#TODO: BLRT und Entropy berechnen!

dat_qwt_sum = dat_qwt_sum %>% 
  left_join(dat_qwt_wide %>% 
              select(pragmaid, cluster)) %>% 
  rename(c(predclass = "cluster"))


dat_pred = dat_qwt_sum %>%
  select(pragmaid, predclass) %>%
  right_join(dat %>%
              filter(period == obs_period,
                     !is.na(interv_id_inner),
                     interv.any ==T)
             )





dat_pred %>% 
  group_by(predclass) %>% 
  mutate(n_class = n_distinct(pragmaid)) %>% 
  ungroup() %>% 
  group_by(pragmaid, predclass, interv.type) %>%
  mutate(num_intervs = n(), more_than_one_interv = num_intervs > 1) %>% 
  group_by(predclass, interv.type) %>% 
  mutate(n_had_interv = n_distinct(pragmaid)) %>% 
  group_by(predclass, interv.type, more_than_one_interv) %>% 
  summarize(n = n_distinct(pragmaid), frac = n/mean(n_had_interv)) %>% 
  ggplot(aes(x = interv.type, y = frac * 100)) +
  geom_col(aes(fill = more_than_one_interv)) +
  facet_wrap(~paste("Cluster", predclass)) +
 # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Intervention", y = "Anteil Personen innerhalb Intervention", fill = "Multiple Interventionen des selben Typs") + 
  coord_flip()



```

```{r}
 
dat_pred2 = dat_pred %>%
  select(pragmaid, predclass) %>%
  distinct() %>% 
  right_join(dat_qwt %>%
  group_by(pragmaid) %>%
  summarize_at(analysis_vars, ~any(.x))) 


# helper function  
get_overlap = function(dat,
                       cls,
                       var1,
                       var2,
                       perspective = c("class", "intervention")){

  
  perspective = match.arg(perspective)
  if(perspective == "class"){
  overlaps = dat %>%
    ungroup() %>% 
    filter(predclass == cls) %>% 
    select(pragmaid, all_of(c(var1,var2))) %>% 
    group_by(pragmaid) %>% 
    summarize(overlap = all(pick(var1),  pick(var2)))
  }
  else{
    dat = dat[c(dat[var1] == TRUE), ]
    overlaps = dat %>%
    ungroup() %>% 
    filter(predclass == cls) %>% 
    select(pragmaid, all_of(c(var1,var2))) %>% 
    group_by(pragmaid) %>% 
    summarize(overlap = all(pick(var1),  pick(var2)))
  }
  
  overlap = sum(overlaps$overlap)/nrow(overlaps)

  # res = data.frame(var = var1, val = overlap) 
  # names(res)[2] = var2
  return(overlap)
}
# helper function end


get_inter_variable_overlaps = function(dat,
                                       cls,
                                       analysis_vars,
                                       perspective =  c("class", "intervention")){
  
perspective = match.arg(perspective)


resresres = data.frame()
for(v1 in analysis_vars){
  resres = data.frame(var = v1)
  
  for(v2 in analysis_vars){
    res = data.frame(val = get_overlap(dat,
                                       cls,
                                       v1,
                                       v2,
                                       perspective = perspective))
    names(res) = v2
    resres = cbind(resres, res)
  }
  
  resresres = rbind(resresres, resres)
}
resresres$predclass = cls
return(resresres)
}





overlaps_class_persp = map_dfr(1:classnum,
                               ~ get_inter_variable_overlaps(
                                            dat_pred2,
                                            cls =.x, 
                                            analysis_vars,
                                            perspective = "class"))


overlaps_interv_persp = map_dfr(1:classnum, 
                                ~ get_inter_variable_overlaps(
                                            dat_pred2,
                                            cls =.x, 
                                            analysis_vars,
                                            perspective = "intervention"))

overlaps_class_persp %>%
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "var2", 
               values_to = "val") %>% 
  mutate(var = as.factor(var), var2 = as.factor(var2)) %>% 
  ggplot(aes(x = reorder(var, desc(var)), y = var2, fill = val)) +
  geom_tile() +
  facet_wrap(~paste0("Cluster ", predclass), scales = "free") +
  geom_text(aes(label = paste0(round(val * 100, 0), "%")), size = 2) +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0)) +
  scale_x_discrete(limits = rev(levels(var))) +
  labs(x = "Anteil Inanspruchnahmen weiterer Intervention",
       y = "Intervention", 
       fill = "Anteil an Klasse [%]")


overlaps_interv_persp %>%
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "var2", 
               values_to = "val") %>% 
    mutate(var = as.factor(var), var2 = as.factor(var2), 
           val = ifelse(is.nan(val), 0, val)) %>% 
  ggplot(aes(x = reorder(var, desc(var)), y = var2, fill = val)) +
  geom_tile() +
  facet_wrap(~paste0("Cluster ", predclass), scales = "free") +
  geom_text(aes(label = paste0(round(val * 100, 0), "%")), size = 1.5) +
  scale_fill_viridis_c() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0)) +
  scale_x_discrete(limits = rev(levels(var))) +
  labs(x = "Intervention",
       y = "Anteil Inanspruchnahme weiterer Intervention",
       fill = "Anteil an X [%]")

```

In more class solutions, it seems to identify slightly different subgroups than the Latent Class solution (see @fig-prop-pp-viz )

Finally a Heatmap, basicly containing the same information as the plot above

```{r, out.width="120%"}
#| title: Heatmap of Hierarchical Clustering Results
#| warning: false
#| message: false

# create a heatmap of the binary data used in the LCA
dat_qwt_wide %>%
  mutate(cluster = cuts) %>%
  select(pragmaid, cluster) %>% 
  left_join(dat_qwt) %>% 
  group_by(cluster, rel_time) %>% 
  summarize_at(all_of(analysis_vars), ~ sum(.x)/length(.x), ) %>% 
  pivot_longer(cols = all_of(analysis_vars),
               names_to = "variable",
               values_to = "value") %>% 
  ggplot(aes(x = rel_time, y = cluster, fill = value)) + 
  geom_tile(show.legend = F) +
  geom_text(aes(label = paste0(round(value, 2)*100,"%")), size = 2.5) +
  theme_minimal() +
  scale_fill_viridis_c() +
  facet_wrap(~variable)

```

## 

## Conclusion

Overall, LCA and Hierarchical Clustering seem to identify similar groups. However, the LCA approach is more sophisticated and can be used to model the data generating process. The hierarchical clustering approach is more exploratory and can be used to identify groups in a more data driven way.

TODO:: Venn Diagramme updaten; Kreuztabelle zeitliche Personen Overlaps

Class probs all time resolutions
